>

### 2016-12-29 paper_drafts/RJournalRevisions/anderson-eason-barnes.Rmd
Update paper draft

The following code gives an example of using a CMIP5 file and some of the R packages and functions discussed. Results include a map of near-surface air temperatures from a single climate model on a specific day in July 2075 (Figure \ref{fig:worldmap}) and a time series of daily near-surface air temperature simulations for the climate model grid point closest to Beijing, China (Figure \ref{fig:timeseries}). To try this example, you will need to download the file "tas_day_GFDL-ESM2G_rcp85_r1i1p1_20710101-20751231.nc" from https://pcmdi.llnl.gov/search/cmip5/ and save it in the "tmp" subdirectory of your home directory.

>>>>

The functions and packages just described can be used to work with CMIP5 netCDF files in R to do things like map near-surface air temperatures from a single climate model on a specific day in July 2075 (Figure \ref{fig:worldmap}) and pull a time series of daily near-surface air temperature simulations for the climate model grid point closest to Beijing, China (Figure \ref{fig:timeseries}). The "starting_from_netcdf" vignette that comes with the "futureheatwaves" package provides all code required to create these figures, as well as more details and code examples on working with CMIP5 netCDF files in R.
